Evolving Dynamics: The U.S. Labor Force from 1972 to 2022 and the Enduring Challenges for Women in the Workplace

### 2024-03-12 paper/paper.qmd
added survey data table

@@

>>>>

```{r}
#| echo: false
#| tbl-cap: Women in the workforce survey data

library(kableExtra)

variable_data <- data.frame( 
  Variable = c("fejobaff", 
               "fehire", 
               "Fefam",
               "Discaffw"), 
  Description = c("For or against preferential hiring of                       women",
                  "Should hire and promote women",
                  "Is it better for man to work, and a woman                    to tend home", 
                  "A woman won't get a job or promotion"), 
  ExampleResponse = c("Strongly Favor", 
              "Disagree", 
              "Agree",
              "Somewhat likely")
)

variable_data %>%
  kbl() %>%
  kable_classic_2(full_width = F)
```

@@

```{r}
